Identifying Failure Inducing Developer Pairs Within Developer Networks

### 2013-03-04 icse-src-2013/paper.tex
FINAL camera ready of SRC 2013

% Research question
With the power of technical dependencies in predicting software failures, the question I
investigated in this project is : 
"\textit{Is it possible to identify pairs of developers whose technical dependencies in code changes
statistically relate to bugs?}"

% Explain our brief intended approach
This paper explains the approach used to locate these pairs of developers in developer networks.
The process utilizes code changes and the call hierarchies effected  to find patterns of developer 
relationships in successful and failed code changes.  These developer relationships can be used
to also promote the idea of leveraging socio-technical congruence, a measure of coordination compared
to technical dependencies amoungst stakeholders, to provide coordination recommendations.

@@

\subsection{Extracting Technical Networks}
% End goal
The basis of this approach is to create a technical network of developers based on method ownership
and those method's call hierarchies effected by code changes. These networks will provide
dependency edges between contributors caused by code changes which may be 
identified as possible failure inducing pairings (Figure~\ref{fig:network}). To achieve this goal,
developer owners of methods, method call hierarchies (technical
dependencies) and code change effects on these hierarchies must be identified.
This approach is described in detail by illustrating its application to mining the data in a Git
repository although it can be used with any software repository.

@@

%Resulting network
These procedures result in a technical network based on contributor method ownership 
inside a call hierarchy effected by a code change (Figure~\ref{fig:network} left hand side).
The network is then simplified by only using edges between developers, since the results
are only interested in discovering the failure inducing edges between developers and not the 
methods themselves (Figure~\ref{fig:network} right hand side). This is the final technical 
network.

@@

\section{Results}
To Illustrate the use of the approach, I conducted a case study of
the Hibernate-ORM project, an open source Java 
application hosted on GitHub\footnote{https://github.com/} with issue tracking 
performed by Jira\footnote{http://www.atlassian.com/software/jira/overview}.

@@

In Hibernate-ORM, 27 statistically significant failure inducing developer pairs (A FI value of 0.5 or higher) 
were found out of a total of 46 statistically significant pairs that existed over the project's lifetime.
The pairings are ranked by their respective FI values (Table~\ref{tab:ratio}). These pairs can be used
to create coordination reccomendations between the developers to catch potential software malfunctions.

>>>>

% Research question
With the power of technical dependencies in predicting software failures, the question I
investigated in this project is : 
``\textit{Is it possible to identify pairs of developers whose technical dependencies in code changes
statistically relate to bugs?}''

% Explain our brief intended approach
This paper explains the approach used to locate these pairs of developers in developer networks.
The process utilizes code changes and the call hierarchies effected  to find patterns of developer 
relationships in successful and failed code changes.  These developer relationships can also be used
to promote the idea of leveraging socio-technical congruence, a measure of coordination compared
to technical dependencies amongst stakeholders, to provide coordination recommendations.

@@

\subsection{Extracting Technical Networks}
% End goal
The basis of this approach is to create a technical network of developers based on method ownership
and those methods' call hierarchies effected by code changes. These networks will provide
dependency edges between contributors caused by code changes which may be 
identified as possible failure inducing pairings (Figure~\ref{fig:network}). To achieve this goal,
developer owners of methods, method call hierarchies (technical
dependencies) and code change effects on these hierarchies must be identified.
This approach is described in detail by illustrating its application to mining the data in a Git
repository although it can be used with any software repository.

@@

%Resulting network
These procedures result in a technical network based on contributor method ownership 
inside a call hierarchy effected by a code change (Figure~\ref{fig:network} left hand side).
The network is then simplified by only using edges between developers, since I
am only interested in discovering the failure inducing edges between developers and not the 
methods themselves (Figure~\ref{fig:network} right hand side). This is the final technical 
network.

@@

\section{Results}
To illustrate the use of the approach, I conducted a case study of
the Hibernate-ORM project, an open source Java 
application hosted on GitHub\footnote{https://github.com/} with issue tracking 
performed by Jira\footnote{http://www.atlassian.com/software/jira/overview}.

@@

In Hibernate-ORM, 27 statistically significant failure inducing developer pairs (FI value of 0.5 or higher) 
were found out of a total of 46 statistically significant pairs that existed over the project's lifetime.
The pairings are ranked by their respective FI values (Table~\ref{tab:ratio}).
